COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
modified H3a results output

## Hypothesis 3a: Subjective values positively predict individual NCS scores.

Intercept:
`r apa_print(hypothesis3a)$estimate$Intercept`

Predictor $AxAUC$:
`r apa_print(hypothesis3a)$estimate$h3_data_axauc`

Fit:
`r apa_print(hypothesis3a)$estimate$modelfit$r2`

$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`

Bayes factor:

$BF10=$ `r extractBF(hypothesis3a_BF)$bf`

>>>>

## Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
